---
title: "[project]_[indicator]"
author:
  name: "Your name"
  affiliation: "Univeristy of Maryland Center of Environmental Science Integration and Application Network"
date: "`r Sys.time()`"
output:
  html_document:
    theme: yeti
    toc: true
---

Purpose: [Please indicate what the data are, and provide a brief description of the indicator data analysis (exploratory or not)].

E.g. For the park walkability indicator, I have Trust for Public Land (TPL) park shapefiles that contain demographic data about populations that can walk to a park in 10 minutes or less. I will average the total population that can walk to a park in 10 min and the diverse group population that can walk to a park in 10 min to make an "Park accessibility" percentage score as the indicator.

# Setup

Explicity define the package versions we use so people in the future can be more successful in rerunning your analysis.

```{r reproducibility}
##run this when first starting your project
#after activation, restore to lockfile
  renv::restore(lockfile = "renv.lock", #file that keeps track of package info
                packages = NULL,
                clean = FALSE) #doesn't delete extra packages laying around


#if you are using different libraries or need to add more than provided
#please update the lockfile so people will know the version you are using

#steps:
#1. use renv::snapshot(), this will look at your current libraries and update
#the renv.lock file that contains package info

#2. Message me (Joe Edgerton) via slack or email and we could update this file
#to the "main" lockfile

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) ##see code and output from chunks
```

```{r download packages, message=FALSE}
##install packages from cran if you need more packages than provided

# my_packages <- c("<your package>")
# 
# install.packages(pkgs = my_packages,
#                  repos = "https://cran.r-project.org")


##for packages on github

#use remotes::install_github(repo = "username/repo-name") 
```

```{r install packages, message=FALSE}
library(tidyverse)
library(here)
library(DBI)
library(RMariaDB)
library(dm)
library(renv)
##list other libraries below that you are using
```


```{r aesthetics}
theme_set(theme_bw) ##using a preset theme for all following plots
##can be overwritten for each plot using theme(...) arguments
```

# data

## db setup

Environmental variables for database (db) access:

Save username and password as environment variables,
this keeps secrets local on your computer and will help with security and
ease of access.

Description:
"Starting with version 1.6, RStudio Connect allows R Environment Variables to be saved at the application level. The variables are encrypted on-disk, and in-memory." [https://db.rstudio.com/best-practices/deployment/]

Follow and run this in your console or in a chunk:

file.edit("~/.Renviron")

Write these into your file with the appropriate project name,
then save the following:

[project]_db_drv = [provided db drv]

[project]_db_name = [provided db name]

[project]_db_username = [provided username]

[project]_db_password = [provided [username password]

[project]_db_host = [provided host]

[project]_db_port = [provided port]

Then follow the code below:

Step 1. Open the connection to the db.

```{r connect to database, eval=FALSE}
##open the connection to the database

conn <- DBI::dbConnect(drv = Sys.getenv("[project]_db_drv"),
               dbname = Sys.getenv("[project]_db_name"),
               username = Sys.getenv("[project]_db_username"),
               password = Sys.getenv("[project]_db_password"),
               host = Sys.getenv("[project]_db_host"),
               port = Sys.getenv("[project]_db_port"),
               sslmode = 'require'
               )
##If everything goes ok, then you should have a
##connection object in your "Environment" window

##You should be good to read/write to the db! Woohoo!
```

Step 1a. (optional) Check out what tables are inside the db and get info about the
db connection.

```{r db information, eval=FALSE}
##check out tables in db
dbListTables(conn)

##check on connection info, if needed
dbGetInfo(conn)

```

Step 2. Read data from the db into your R environment so you can work on it.

```{r db read data, eval=FALSE}
##to access data inside the db
table_you_need <- dbReadTable(conn = conn, "[table you need in db]")

```

Step 3. Write data from a file or from a data frame and send to the db. This step is divided into two parts below.

```{r db write data, eval=FALSE}

##Part 1

test <- dm(df) %>% ##create a dm object to prepare you data to go to the database.
  dm_add_pk(df, ID) ##need to establish a primary key (unique ID for each row)

##Part 2

copy_dm_to(dest = conn, ##specifies the connection object for the database
             dm = test, ##specifies the table to send to the database
             temporary = FALSE, ##you want this to be permanent
             table_names = ~"my test table") ##what will people search for and see in the db? Please appropriately name tables to avoid confusion.

```

Now you can begin to import, clean, upload, and analyze your indicator data.

## Import (CSVs, Excel sheets, APIs, etc.)

Import data that will eventually go into the db.

```{r data import}
##load files into a data folder using: here("data", "[indicator]")

```

## clean

Clean or extract data from the files to make into tables for upload.

```{r tidy/transform data}
# [https://r4ds.had.co.nz/tidy-data.html] is a good chapter to refer to tidy data 

```

## db

```{r upload data to be reference below}
#see Step 3. for upload instruction

```

## analysis

```{r}

```

# SUPER IMPORTANT

```{r, eval=FALSE}
##please disconnect from the database when you're done using it, thanks!
dbDisconnect(conn)
```